\thetitle

### 2025-05-13 workshop/introduction.tex
fix

Pigeons.jl\footnote{The source code for Pigeons.jl can be found at 
\url{https://github.com/Julia-Tempering/Pigeons.jl}. 
Pigeons.jl v0.2.0, used in the example scripts below, is compatible with Julia 1.8+.}
enables users to sample efficiently from challenging probability distributions 
and solve integration problems by 
implementing state-of-the-art sampling algorithms \cite{syed2021nrpt,surjanovic2022vpt} 
that leverage distributed computation. Its simple user interface facilitates performing such computations 
single-threaded, multi-threaded, and/or distributed over MPI-communicating machines. 
We have stress-tested Pigeons successfully with up to 1000 machines running 
concurrently on a compute cluster (Sockeye) at the University of British Columbia.
Importantly, Pigeons comes with guarantees on \emph{strong parallelism invariance} (SPI), 
wherein the output for a given seed is \emph{identical} irrespective of the number 
of threads or processes. Such a level of reproducibility is rare in distributed 
software but of great use for the purposes of debugging in the context of sampling 
algorithms, which produce stochastic output.
Specifically, Pigeons.jl is designed to be suitable and yield reproducible output for:
\begin{enumerate}
    \item one machine running on one thread;
    \item one machine running on several threads;
    \item several machines running, each using one thread, and
    \item several machines running, each using several threads.
\end{enumerate}

>>>>

Pigeons.jl\footnote{The source code for Pigeons.jl can be found at 
\url{https://github.com/Julia-Tempering/Pigeons.jl}. 
Pigeons.jl v0.2.0, used in the example scripts below, is compatible with Julia 1.8+.}
enables users to sample efficiently from challenging probability distributions 
and solve integration problems by 
implementing state-of-the-art sampling algorithms \cite{syed2021nrpt,surjanovic2022vpt} 
that leverage distributed computation. Its simple user interface facilitates performing such computations 
single-threaded, multi-threaded, and/or distributed over MPI-communicating machines. 
We have stress-tested Pigeons successfully with up to 1000 processes running 
concurrently on a compute cluster (Sockeye) at the University of British Columbia.
Importantly, Pigeons comes with guarantees on \emph{strong parallelism invariance} (SPI), 
wherein the output for a given seed is \emph{identical} irrespective of the number 
of threads or processes. Such a level of reproducibility is rare in distributed 
software but of great use for the purposes of debugging in the context of sampling 
algorithms, which produce stochastic output.
Specifically, Pigeons.jl is designed to be suitable and yield reproducible output for:
\begin{enumerate}
    \item one machine running on one thread;
    \item one machine running on several threads;
    \item several machines running, each using one thread, and
    \item several machines running, each using several threads.
\end{enumerate}
